---
title: "Побудова прогнозів із використанням Facebook Prophet"
---

Це лише заготовка, сторінка роботі.

```{r, echo = FALSE, results = 'hide'}
knitr::opts_chunk$set(fig.retina=2, fig.path = "fig_forecast_prophet/")
Sys.setlocale(category="LC_ALL",locale="uk_UA.utf8" )
```


```{r}
library(tidyverse)
library(prophet)


```

# Prophet

https://facebook.github.io/prophet/docs/quick_start.html#r-api

First we read in the data and create the outcome variable. As in the
Python API, this is a dataframe with columns ds and y, containing the
date and numeric value respectively. The ds column should be
YYYY-MM-DD for a date, or YYYY-MM-DD HH:MM:SS for a timestamp. As
above, we use here the log number of views to Peyton Manning’s
Wikipedia page, available here.

```{r}
df <- read_csv('../covid19_by_area_type_hosp_dynamics.csv')
df <- df %>%
    select(zvit_date, new_confirm) %>%
    group_by(zvit_date) %>%
    summarise(new_confirm = sum(new_confirm)) %>%
    filter(zvit_date > as.Date("2020-04-01"))

df <- df %>% rename(ds = zvit_date, y = new_confirm)

head(df)
plot(df)
```

We call the prophet function to fit the model. The first argument is
the historical dataframe. Additional arguments control how Prophet
fits the data and are described in later pages of this documentation.

```{r}
m <- prophet(df)
```

Predictions are made on a dataframe with a column ds containing the
dates for which predictions are to be made. The make_future_dataframe
function takes the model object and a number of periods to forecast
and produces a suitable dataframe. By default it will also include the
historical dates so we can evaluate in-sample fit.


```{r}
future <- make_future_dataframe(m, periods = 14)
tail(future)
```

As with most modeling procedures in R, we use the generic predict
function to get our forecast. The forecast object is a dataframe with
a column yhat containing the forecast. It has additional columns for
uncertainty intervals and seasonal components.

```{r}
forecast <- predict(m, future)
tail(forecast[c('ds', 'yhat', 'yhat_lower', 'yhat_upper')])
```

You can use the generic plot function to plot the forecast, by passing
in the model and the forecast dataframe.

```{r}
plot(m, forecast)
```

You can use the prophet_plot_components function to see the forecast
broken down into trend, weekly seasonality, and yearly seasonality.

```{r}
prophet_plot_components(m, forecast)
```

More details about the options available for each method are available
in the docstrings, for example, via `?prophet` or `?fit.prophet`. This
documentation is also available in the [reference
manual](https://cran.r-project.org/web/packages/prophet/prophet.pdf)
on CRAN.

[Повернутись на головну](index.html) або [повідомити про
помилку]((https://github.com/vityok/covid19_ua/issues))
